---
title: "Text Mining on Survey Answers"
author: "JCB"
date: "August 5, 2020"
output: html_document
---

Getting the Libraries
```{r}
library(rio)
library(tm)
library(NLP)
library(dplyr)
library(wordcloud)
library(RColorBrewer)
library(anchors)
library(readxl)
```

Creating the dataset
```{r}
Survey <- read_excel("C:/Users/Jesus/Desktop/Analytics/R/Projects/Survey.xlsx")
View(Survey)
```

Why Column Analysis




Converting the text of the columns into Corpus
```{r}
Why <- iconv(Survey$Why, to = "UTF-8")
Why <- (VectorSource(Why))
Why <- Corpus(Why)
inspect(Why[1:5])
```

Cleaning the text
```{r}
CWhy <- tm_map(Why, tolower)
CWhy <- tm_map(CWhy, removePunctuation)
CWhy <- tm_map(CWhy, removeNumbers)
CWhy <- tm_map(CWhy, removeWords, stopwords("english"))
CWhy <- tm_map(CWhy, removeWords, c("crowddoing" ))
CWhy <- tm_map(CWhy,stripWhitespace)
CWhy <- tm_map(CWhy,gsub, pattern = "â???¦", replacement = "")
head(CWhy)
```


Creating the TDM and removing duplicate counts
```{r}
MATWhy <- as.matrix(TermDocumentMatrix(CWhy))
range(MATWhy)
MATWhy2 <- data.frame(MATWhy)
namesWhy <- colnames(MATWhy2)
MATWhy3 <- replace.value(data = MATWhy2, names = namesWhy, from = 2, to = 1)
MATWhy3 <- replace.value(data = MATWhy3, names = namesWhy, from = 3, to = 1)
MATWhy3 <- replace.value(data = MATWhy3, names = namesWhy, from = 4, to = 1)
MATWhy3 <- replace.value(data = MATWhy3, names = namesWhy, from = 5, to = 1)
```

Creating the WordCloud
```{r}
WhyWC <- rowSums(MATWhy3)
head(WhyWC)
WhyWC <- subset(WhyWC, WhyWC>=4)
namesWhyWC <- names(WhyWC)
FinalWhyWC <- data.frame(namesWhyWC, as.numeric(WhyWC))
wordcloud(words = FinalWhyWC$namesWhyWC, freq = FinalWhyWC$as.numeric.WhyWC., max.words = 1000, random.order = FALSE, rot.per = 0, random.color= FALSE, colors = brewer.pal(n = length(FinalWhyWC$namesWhyWC), name = "BuPu"))
```
```

Extracting the comments that contain the top words and creating an excel for the word counts
```{r}
TMW3 <- t(MATWhy3)
TMW3 <- data.frame(TMW3)
SkillsWC <- which(TMW3$skills >= 1)
WhySkills <- Survey[as.numeric(SkillsWC),]
export(WhySkills, "C:/Users/Jesus/Desktop/Analytics/R/Projects/AnswersWhySkills.xlsx")
export(FinalWhyWC, "C:/Users/Jesus/Desktop/Analytics/R/Projects/WordsWhy.xlsx")
```

